### 2016-01-20 paper.tex
Move strut drag before wake in abstract
Use lambda_0
Add Martin's email address and complete addresses; resolves #47

{\Large \textbf\newline{Experimental study of a low solidity cross-flow turbine
        at transitional Reynolds numbers: Power production, strut losses, and near-wake
        dynamics}} \newline % Insert author names, affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O.
Box 5800, Albuquerque, New Mexico 87185-MS1124 \\ \bigskip

% Use the asterisk to denote corresponding authorship and provide email address
% in note below.
* pxL3@unh.edu

@@

The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
physical reference model vertical-axis cross-flow turbine were measured
experimentally in a towing tank, to provide a comprehensive open dataset for
validating numerical models. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed. Weak linear $Re$-dependence was achieved
at a turbine diameter Reynolds number $Re_D \approx 10^6$. An optimal tip speed
ratio $\lambda_0 = 3.1$ was chosen, at which the near wake velocity was measured
at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence kinetic energy, and
mean kinetic energy transport were compared with results from a high solidity
turbine acquired with the same test apparatus. Overall, lower levels of
streamwise wake recovery were calculated for the RM2 case---a consequence of
both the relatively low solidity and tapered blades reducing blade tip vortex
shedding---responsible for mean vertical advection---and lower levels of
turbulence caused by higher operating tip speed ratio and therefore reduced
dynamic stall. The effects of blade support strut drag on turbine performance
were investigated by covering the rotor's NACA 0021 struts with cylinders. As
expected, this modification drastically reduced the rotor power coefficient.
Strut drag was also measured for the NACA 0021 and cylindrical configurations
with the blades removed.

@@

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine due to the lower rotor drag coefficient
and a slightly blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is
relatively weaker, which is likely an effect of the RM2's smaller blade chord
length and tapered blades.

>>>>

{\Large \textbf\newline{Experimental study of a low solidity cross-flow turbine
        at transitional Reynolds numbers: Power production, strut losses, and near-wake
        dynamics}} \newline % Insert author names, affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O.
Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

% Use the asterisk to denote corresponding authorship and provide email address
% in note below.
*pxL3@unh.edu (PB), *martin.wosnik@unh.edu (MW)

@@

The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
physical reference model vertical-axis cross-flow turbine were measured
experimentally in a towing tank, to provide a comprehensive open dataset for
validating numerical models. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed. Weak linear $Re$-dependence was achieved
at a turbine diameter Reynolds number $Re_D \approx 10^6$. The effects of blade
support strut drag on turbine performance were investigated by covering the
rotor's NACA 0021 struts with cylinders. As expected, this modification
drastically reduced the rotor power coefficient. Strut drag was also measured
for the NACA 0021 and cylindrical configurations with the blades removed. An
optimal tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the near wake
velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence
kinetic energy, and mean kinetic energy transport were compared with results
from a high solidity turbine acquired with the same test apparatus. Overall,
lower levels of streamwise wake recovery were calculated for the RM2 case---a
consequence of both the relatively low solidity and tapered blades reducing
blade tip vortex shedding---responsible for mean vertical advection---and lower
levels of turbulence caused by higher operating tip speed ratio and therefore
reduced dynamic stall.

@@

The mean velocity field at the chosen optimal tip speed ratio $\lambda_0=3.1$, 1
m downstream ($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean
streamwise velocity deficit is markedly more symmetric than that of the
UNH-RVAT, with lower acceleration around the turbine due to the lower rotor drag
coefficient and a slightly blockage ratio \cite{Bachant2015-JoT}. Tip vortex
shedding is relatively weaker, which is likely an effect of the RM2's smaller
blade chord length and tapered blades.
